% Copyright (c) 2011-2023, Corey Oliver, corey.jon.oliver@gmail.com

% Permission to use, copy, modify, and/or distribute this software for
% any purpose with or without fee is hereby granted, provided that the
% above copyright notice and this permission notice appear in all
% copies.

% THE SOFTWARE IS PROVIDED “AS IS” AND THE AUTHOR DISCLAIMS ALL
% WARRANTIES WITH REGARD TO THIS SOFTWARE INCLUDING ALL IMPLIED
% WARRANTIES OF MERCHANTABILITY AND FITNESS. IN NO EVENT SHALL THE
% AUTHOR BE LIABLE FOR ANY SPECIAL, DIRECT, INDIRECT, OR CONSEQUENTIAL
% DAMAGES OR ANY DAMAGES WHATSOEVER RESULTING FROM LOSS OF USE, DATA OR
% PROFITS, WHETHER IN AN ACTION OF CONTRACT, NEGLIGENCE OR OTHER
% TORTIOUS ACTION, ARISING OUT OF OR IN CONNECTION WITH THE USE OR
% PERFORMANCE OF THIS SOFTWARE.

% Jason R. Blevins - Curriculum Vitae
% 
% Copyright (C) 2004-2011 Jason R. Blevins
% 
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[subtle]{savetrees}

% Fonts
\usepackage[T1]{fontenc}
% \usepackage[urw-garamond]{mathdesign}

% Set your name here
\def\name{Corey J. Oliver}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {computer science, software development, software engineering},
  pdftitle = {\name: Resume},
  pdfsubject = {Resume},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\large}
\subsectionfont{\rmfamily\mdseries\itshape\normalsize} % chktex 6

% Other possible font commands include:
% \mdseries for default,
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0.25em}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0.25em}
    }
  }{
  \end{list}
}

% Make lists with bullets
\newenvironment{bitemize}{
  \begin{list}{\(\bullet \)}{
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0.25em}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0.25em}
    }
  }{
  \end{list}
}

\newcommand{\yearrange}[1]{\hfill \textbf{#1} \par}

\begin{document}

% Place name at left
% {\huge \name}

% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}

\bigskip

\centerline{Independence, IA | (641) 780-9596 | % chktex 8
  \href{mailto:corey.jon.oliver@gmail.com}{corey.jon.oliver@gmail.com} |
  \href{http://coreyoliver.org/}{http://coreyoliver.org/}}

\hrulefill{}

\bigskip

\centerline{\bf SENIOR SOFTWARE DEVELOPER}

\bigskip

\noindent
Accomplished Senior Software Developer with 11+ years of experience in
fast-paced software development. Excels in every stage of the life cycle of
software development, including design, creation, coding, debugging, testing and
maintenance. Expert in devising innovative and tailored solutions. Proven track
record of achieving exceptional results in developing for complex,
interconnected systems and providing reliable, secure solutions to help
businesses achieve their goals. Advanced skills and knowledge of leading
programming tools.

\section*{Technical Knowledge}
\begin{itemize}
  \item \textbf{Languages.} Scala, Java, Python, C$^\sharp$, Bash,
        Javascript, Ruby, Groovy
  \item \textbf{Tools.} Jenkins, Terraform, Snyk, Docker
\end{itemize}

\section*{Education}

\begin{itemize}
  \item \textbf{M.C.S.}, University of Iowa
  \item \textbf{B.A.} Computer Science, \textit{Magna Cum Laude}, Central
        College, Pella, IA
        \begin{itemize}
          \item \textit{Study Abroad:} Hangzhou, China and
                London, England
        \end{itemize}
\end{itemize}

\section*{Professional Experience}

\subsection*{Dwolla Inc, Des Moines, IA}

\begin{itemize}
  \item \textbf{Senior Software Developer} \yearrange{Jan 2019--Present}
        \begin{bitemize}
          \item Created, tested, and implemented a strategy for building and deploying
          Windows Docker images of our services to AWS which included successfully
          migrating a pilot service without impacting production. This resulted in
          significant cost and time savings by eliminating the need for manual
          updates and maintenance required with our previous service deployment
          method.
          \item Developed a configuration as code solution using a custom-built
          Jenkins shared library, similar to Circle-CI, Travis CI, and GitHub
          actions, and implemented a gatekeeping feature for deployments to certain
          environments based on the branch being processed. This improved efficiency
          and automation of the build and deployment process, reducing the risk of
          errors and increasing the speed of service releases.
          \item Wrote and executed an internal RFC that proposed an incremental
          implementation of Scala Steward, a bot that keeps Scala library
          dependencies up-to-date, with a focus on minimally impacting developer
          workflow. Recieved and addressed feedback to the proposal. This ensured
          services would automatically recieve security and performance updates,
          leading to a decrease in developer cost and time.
        \end{bitemize}
\end{itemize}

\begin{itemize}
  \item \textbf{Software Developer} \yearrange{May 2012--Jan 2019}
        \begin{bitemize}
          \item Led a team in migrating a legacy transaction storage system to an
          event-sourced system, resulting in the ability to perform real-time
          reconciliation and other critical business tasks, while minimizing
          disruption to production systems through a phased approach and regular
          communication with stakeholders.
          \item Assisted in the design, development and implementation of a data
          collation solution that used customer, transaction and other data that was
          sent to a 3rd party service for processing, resulting in improved fraud
          detection and compliance with the company's audit and regulatory
          obligations.
          \item Contributed to the Level One Project, an initiative led by the Gates
          Foundation to enable payments and financial inclusion in poorer countries,
          by assisting in the development of the central ledger component
          responsible for recording and settling transfers.
        \end{bitemize}
\end{itemize}

\subsection*{Alliance Technologies, Des Moines, IA}

\begin{itemize}
  \item \textbf{Software Developer} \yearrange{Summer 2010}
        \begin{bitemize}
          \item Developed and supported \textbf{FullCount}, a touchscreen enabled
          point of sale system used in retirement communities % In
          collaboration with with Susan Anderson and Anshul Kumaria.
          \item Conceptualized a FullCount component using the Javascript framework
          Dojo which enabled users to design restaurant table layouts
          \item Created a web interface to remotely gather information on and monitor
          remote company distributed FullCount machines
        \end{bitemize}
\end{itemize}

\section*{Research}

\subsection*{University of Iowa, Department of Computer Science}

\begin{itemize}
  \item \textbf{Research Assistant} \yearrange{Spring--Summer 2011 % chktex 8
          \& Spring 2012}
        \textit{Aaron Stump} (Advisor)
        \begin{bitemize}
          \item Implemented and verified properties of a graph data structure in the
          programming language \textbf{Guru}, a pure functional programming language
          for writing formal proofs demonstrating the properties of programs
          \item Proved formal properties of the software program \textbf{versat}, A
          formally verified SAT solver incorporating the essential features of modern
          SAT solvers, including clause learning, watched literals, optimized conflict
          analysis, non-chronological backtracking and backjumping
          % In collaboration with Duckki Oe, Aaron Stump and Keven Clancy.
          \item Evaluated and tested versat against leading SAT solvers
          \item Researched and implemented a term indexing data structure for the
          software program \textbf{gtrw}, A parser generator based on term-rewriting
          % In collaboration with Aaron Stump and JJ Meyer.
          \item Refactored and improved gtrw codebase to improve overall runtime
          performance for rewriting terms
          % \item \textbf{LFSC}, A high-performance proof checker for LFSC (``Logical
          %   Framework with Side Conditions''), a meta-language for encoding proof
          %   systems. In collaboration with Aaron Stump and Andrew Reynolds.
        \end{bitemize}
  \item \textbf{Research Assistant} \yearrange{Summer 2011} \textit{Cesare
          Tinelli} (Mentor)
        \begin{bitemize}
          \item Built a lexer and parser for the programming language Lustre for use in
          the front-end component of \textbf{KIND2}, An automatic verification tool
          for safety properties of Lustre programs
          % In collaboration with Temesghen Kahsai and Cesare Tinelli.
          \item Implemented code transformations for the KIND2 front-end of Lustre
          source code such as global \texttt{const} and \texttt{type} propagation,
          recursive expansion of \texttt{include} statements, and node call expansion
          \item Verified soundness of code transformation by writing a shell script to
          compare compilation output of transformed and untransformed Lustre source
          files
        \end{bitemize}
\end{itemize}

\section*{Publications}

\subsection*{Refereed Conferences and Workshops}

\begin{itemize}
  {\item Aaron Stump, Andrew Reynolds, Cesare Tinelli, Austin Laugesen, Harley
        Eades, Corey Oliver, Ruoyu Zhang. \textbf{LFSC for SMT Proofs: Work in
          Progress}. In Proceedings of the 2nd International Workshop on Proof
        eXchange for Theorem Proving (PxTP'12), Manchester, UK, 2012.}
\end{itemize}

\begin{itemize}
  {\item Duckki Oe, Aaron Stump, Corey Oliver and Kevin Clancy. \textbf{A
          Verified Modern SAT Solver}. In Proceedings of the 13th International
        Conference on Verification, Model Checking, and Abstract Interpretation
        (VMCAI'12), Philadelphia, Pennsylvania, 2012.}
\end{itemize}

\medskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\end{document}
